---
title: "Get the templates and render them"
author: "E. Reynolds"

---

These templates reside online in package github repositories.  All are xaringan .Rmd files that have flipbookr in use. 


```{r, results='hide'}
# templates from flipbookr:

minimal_flipbook <- "https://raw.githubusercontent.com/EvaMaeRey/flipbookr/master/inst/rmarkdown/templates/minimal-flipbook/skeleton/skeleton.Rmd"

most_features_flipbook <- "https://raw.githubusercontent.com/EvaMaeRey/flipbookr/master/inst/rmarkdown/templates/most-features/skeleton/skeleton.Rmd"

python_flipbook <- "https://raw.githubusercontent.com/EvaMaeRey/flipbookr/master/inst/rmarkdown/templates/python-flipbook/skeleton/skeleton.Rmd"

# need some fixing up!
# essay_exploder <- "https://raw.githubusercontent.com/EvaMaeRey/flipbookr/master/inst/rmarkdown/templates/slow-essay/skeleton/skeleton.Rmd"

# template from ggxmeans:

ggxmean_template <- "https://raw.githubusercontent.com/EvaMaeRey/ggxmean/master/inst/rmarkdown/templates/template-name/skeleton/skeleton.Rmd"
```

We download each.

```{r}
# Download them all and create double crochet version
unlink("templates", recursive = T)
dir.create("templates")

list_of_urls <- objects()
list_of_paths <- paste0("templates/", 
                       list_of_urls, 
                       ".Rmd")

for (i in 1:length(list_of_urls)){

  download.file(get(list_of_urls[i]), list_of_paths[i])
  doublecrochet::crochet(list_of_paths[i])

  }

# embedding is different in king html_document
# and we won't use double crochet on it so separate
embed_flipbook <- "https://raw.githubusercontent.com/EvaMaeRey/flipbookr/master/inst/rmarkdown/templates/flipbook-embed/skeleton/skeleton.Rmd"

download.file(embed_flipbook, "templates/embed_flipbook.Rmd")




```

Not a great idea to use `rmarkdown::render()` from within Rmarkdown.  From the book:

> In case you need to render an Rmd document inside another Rmd document, we strongly recommend that you use this method instead of directly calling rmarkdown::render() in a code chunk, because rmarkdown::render() creates and relies on a lot of side effects internally, which may affect rendering other Rmd documents in the same R session.

Feeling a bit lazy to learn new method. Instead, the approach below:

```{r, eval = F}
library(magrittr)
list.files("templates") %>% 
  paste0("templates/",.) %>% 
  paste0("rmarkdown::render('",., "'); rm(list=ls())") %>% 
  paste0(collapse = "\n") %>% 
  writeLines("to_do.R")

# Then execute in console:
# source("to_do.R")
```

