---
title: "Embedded Flipbook"
author: Me, an Rmarkdown writer and flipbook builder
output: html_document
---

---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
title: "Embedded Flipbook"\nauthor: Me, an Rmarkdown writer and flipbook builder\noutput: html_document')
```


---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\nThis template aimed at doing the following:  preparing a flipbook from within an .Rmd source file and then *embedded* it in the resulting html.  Narrative might be interspersed between the code-movies.  \n\n## Steps:\n\n#### 1. Write a code chunk. \n#### 2. Use embed_flipbook() to create chunk\'s flipbook and embed in your html_document \n\n## More detail about step 2:\n\n#### 2.a. save that chunk code out as text and the current global environment\n#### 2.b. create an .Rmd file that will bring in code and global environment\n#### 2.c. render that file to an html (xaringan slide show)\n#### 2.d. embed the flipbook upon knitting your working .Rmd to .html\n\n\n```{r setup, include = F}\n# This is the recommended set up for flipbooks\n# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming\noptions(knitr.duplicate.label = "allow")\nknitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = F, error = F)\nlibrary(flipbookr)\nlibrary(tidyverse)\n```\n\n```{r just_for_evamaerey, cache = FALSE, echo = FALSE, message=F, warning=F}\n# you can just delete this whole code chunk -- it\'s just for testing and developing the package\ntry(source("../../../../../R/a_create_test_code.R"))\ntry(source("../../../../../R/b_parsing.R"))\ntry(source("../../../../../R/c_prep_sequences.R"))\ntry(source("../../../../../R/d_prep_rmd_chunks.R"))\ntry(source("../../../../../R/e_define_css.R"))\ntry(source("../../../../../R/f_chunk_expand.R"))\ntry(source("../../../../../R/g_exported_functions.R"))\ntry(source("../../../../../R/h_write_instant_flipbook.R"))\n```\n\n\n# A1. Here is some code (I\'m naming the chunk "my_code"): \n\nYou might think about setting this code chunk\'s option include = F, to hide the code and output.\n\n```{r my_code}\ncars %>% \n  ggplot() +\n  aes(x = dist) +\n  aes(y = speed) +\n  geom_point() -> \ng\n```\n\n\n\n# A2. Let\'s get a walk-through using embed_flipbook():\n\nYou might want to set the code chunk options to echo = F, unless you are demoing embed_flibook(). \n\n```{r}\nembed_flipbook(chunk_name = "my_code", \n                       use_share_again = T,\n                       font_size = 120)\n```\n')
```
---

This template aimed at doing the following:  preparing a flipbook from within an .Rmd source file and then *embedded* it in the resulting html.  Narrative might be interspersed between the code-movies.  

## Steps:

#### 1. Write a code chunk. 
#### 2. Use embed_flipbook() to create chunk's flipbook and embed in your html_document 

## More detail about step 2:

#### 2.a. save that chunk code out as text and the current global environment
#### 2.b. create an .Rmd file that will bring in code and global environment
#### 2.c. render that file to an html (xaringan slide show)
#### 2.d. embed the flipbook upon knitting your working .Rmd to .html


```{r setup, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
options(knitr.duplicate.label = "allow")
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = F, error = F)
library(flipbookr)
library(tidyverse)
```

```{r just_for_evamaerey, cache = FALSE, echo = FALSE, message=F, warning=F}
# you can just delete this whole code chunk -- it's just for testing and developing the package
try(source("../../../../../R/a_create_test_code.R"))
try(source("../../../../../R/b_parsing.R"))
try(source("../../../../../R/c_prep_sequences.R"))
try(source("../../../../../R/d_prep_rmd_chunks.R"))
try(source("../../../../../R/e_define_css.R"))
try(source("../../../../../R/f_chunk_expand.R"))
try(source("../../../../../R/g_exported_functions.R"))
try(source("../../../../../R/h_write_instant_flipbook.R"))
```


# A1. Here is some code (I'm naming the chunk "my_code"): 

You might think about setting this code chunk's option include = F, to hide the code and output.

```{r my_code}
cars %>% 
  ggplot() +
  aes(x = dist) +
  aes(y = speed) +
  geom_point() -> 
g
```



# A2. Let's get a walk-through using embed_flipbook():

You might want to set the code chunk options to echo = F, unless you are demoing embed_flibook(). 

```{r}
embed_flipbook(chunk_name = "my_code", 
                       use_share_again = T,
                       font_size = 120)
```



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n# B1. Here is some more code; I\'m named the code chunk "fine_tuning":\n\nYou might just set the code chunk options include = F.\n\n```{r fine_tuning, fig.show=\'hide\'}\ng + \n  theme_minimal(base_size = 12) +\n  aes(size = dist) +\n  aes(color = dist) +\n  scale_color_viridis_c() + \n  geom_smooth() +\n  theme(legend.position = \n          "none") +\n  labs(x = "Distance") +\n  labs(y = "Speed") + #BREAK\n  labs(title = "Cool plot!") +\n  theme(plot.title.position = \n          "plot") #BREAK\n```\n\n# B2. Let\'s look at the build created from  embed_flipbook. View below or view [in new tab](fine_tuning.html){target="_blank"}\n\nYou might set the code chunk option echo = F\n\n```{r}\nembed_flipbook(chunk_name = "fine_tuning", \n               use_share_again = T, \n               use_embed_xaringan = T,\n               font_size = 100,\n               title_page = T,\n               title = "How to Style your Plot",\n               subtitle = "Thematic Adjustments",\n               author = "Reynolds Lab",\n               break_type = "user")\n```\n\n\n\n# C. Okay python!  Just kidding.  This doesn\'t work yet.\n')
```
---

# B1. Here is some more code; I'm named the code chunk "fine_tuning":

You might just set the code chunk options include = F.

```{r fine_tuning, fig.show='hide'}
g + 
  theme_minimal(base_size = 12) +
  aes(size = dist) +
  aes(color = dist) +
  scale_color_viridis_c() + 
  geom_smooth() +
  theme(legend.position = 
          "none") +
  labs(x = "Distance") +
  labs(y = "Speed") + #BREAK
  labs(title = "Cool plot!") +
  theme(plot.title.position = 
          "plot") #BREAK
```

# B2. Let's look at the build created from  embed_flipbook. View below or view [in new tab](fine_tuning.html){target="_blank"}

You might set the code chunk option echo = F

```{r}
embed_flipbook(chunk_name = "fine_tuning", 
               use_share_again = T, 
               use_embed_xaringan = T,
               font_size = 100,
               title_page = T,
               title = "How to Style your Plot",
               subtitle = "Thematic Adjustments",
               author = "Reynolds Lab",
               break_type = "user")
```



# C. Okay python!  Just kidding.  This doesn't work yet.



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n```{python hello_python, include = T}\n[1, 4] * 8\n\n3 + 4 * 8 \n\n2 + 6\n\n4 * 8\n\n[1,2] + [3,4,5,6]\n\n["hello", "world!", 1, 2, 3] * 2\n\nimport numpy as np\n\nnp.reshape(np.arange(1,25), \n    (4,3,2), "F")\n```\n\n\n\n```{r, eval = F}\nembed_flipbook("hello_python",\n               lang = "python")\n```\n\n\n# D. Text flipbook subject to change:\n\n```{r}\nembed_text_flipbook("hi there good seeing you", \n                    title = "greetings", \n                    sep = " ",\n                    use_embed_xaringan = T)\n```\n\n\n\n\n\n\n```{css, eval = TRUE, echo = FALSE}\n.remark-code{line-height: 1.5; font-size: 80%}\n\n@media print {\n  .has-continuation {\n    display: block;\n  }\n}\n```')
```
---

```{python hello_python, include = T}
[1, 4] * 8

3 + 4 * 8 

2 + 6

4 * 8

[1,2] + [3,4,5,6]

["hello", "world!", 1, 2, 3] * 2

import numpy as np

np.reshape(np.arange(1,25), 
    (4,3,2), "F")
```



```{r, eval = F}
embed_flipbook("hello_python",
               lang = "python")
```


# D. Text flipbook subject to change:

```{r}
embed_text_flipbook("hi there good seeing you", 
                    title = "greetings", 
                    sep = " ",
                    use_embed_xaringan = T)
```






```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 80%}

@media print {
  .has-continuation {
    display: block;
  }
}
```
