---
title: "{ggxmean}"
author: "Your Name"
date: "The Date"
output: 
  xaringan::moon_reader:
    lib_dir: libs
    seal: FALSE
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
title: "{ggxmean}"\nauthor: "Your Name"\ndate: "The Date"\noutput: \n  xaringan::moon_reader:\n    lib_dir: libs\n    seal: FALSE\n    css: [default, hygge, ninjutsu]\n    nature:\n      ratio: 16:9\n      highlightStyle: github\n      highlightLines: true\n      countIncrementalSlides: false')
```


---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\nclass: inverse\nbackground-image: url(https://images.unsplash.com/photo-1572291720677-d8d28ac52a5b?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1556&q=80)\nbackground-size: cover\n\n# [{ggxmean}](https://github.com/EvaMaeRey/ggxmean)\n<br><br><br><br><br>\n<br><br><br><br><br>\n<br><br><br><br><br>\n<br><br><br><br><br>\n#### Photo credit: Hans Veth\n\n\n```{r, include = F}\n# This is the recommended set up for flipbooks\n# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming\nknitr::opts_chunk$set(fig.width = 8, message = FALSE, warning = FALSE, comment = "", cache = T)\nlibrary(flipbookr)\nlibrary(tidyverse)\n```\n\n\n')
```
---


class: inverse
background-image: url(https://images.unsplash.com/photo-1572291720677-d8d28ac52a5b?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1556&q=80)
background-size: cover

# [{ggxmean}](https://github.com/EvaMaeRey/ggxmean)
<br><br><br><br><br>
<br><br><br><br><br>
<br><br><br><br><br>
<br><br><br><br><br>
#### Photo credit: Hans Veth


```{r, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 8, message = FALSE, warning = FALSE, comment = "", cache = F)
library(flipbookr)
library(tidyverse)
```





---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
class: inverse, center, middle\n\n# viz the mean and conditional means\n\n')
```
---
class: inverse, center, middle

# viz the mean and conditional means




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\n`r chunk_reveal("vizthemean1d", break_type = "user")`\n\n```{r vizthemean1d, include = F}\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  drop_na() %>% \n  ggplot() +\n  aes(x = bill_length_mm) +\n  geom_rug(alpha = .3) +\n  geom_histogram(alpha = .4) + #BREAK\n  geom_xmean() + #BREAK\n  aes(color = species) + #BREAK\n  aes(fill = species) + #BREAK\n  facet_grid(rows = vars(species)) + #BREAK\n  facet_grid(rows = vars(species, sex)) + #BREAK\n  geom_rug(alpha = .6) + #BREAK\n  geom_xmin(linetype = "dashed") + #BREAK\n  geom_xmax(color = "goldenrod") + #BREAK\n  geom_xmedian(color = "black") + #BREAK\n  ggxmean:::geom_xq2575(\n    linetype = "dotted",\n    color = "black",\n    size = .75) + #BREAK\n  geom_boxplot(y = 0,\n               width = 3,\n               fill = "white",\n               color = "black") #BREAK\n```\n\n\n\n')
```
---


`r chunk_reveal("vizthemean1d", break_type = "user")`

```{r vizthemean1d, include = F}
library(tidyverse)
library(ggxmean)
palmerpenguins::penguins %>% 
  drop_na() %>% 
  ggplot() +
  aes(x = bill_length_mm) +
  geom_rug(alpha = .3) +
  geom_histogram(alpha = .4) + #BREAK
  geom_xmean() + #BREAK
  aes(color = species) + #BREAK
  aes(fill = species) + #BREAK
  facet_grid(rows = vars(species)) + #BREAK
  facet_grid(rows = vars(species, sex)) + #BREAK
  geom_rug(alpha = .6) + #BREAK
  geom_xmin(linetype = "dashed") + #BREAK
  geom_xmax(color = "goldenrod") + #BREAK
  geom_xmedian(color = "black") + #BREAK
  ggxmean:::geom_xq2575(
    linetype = "dotted",
    color = "black",
    size = .75) + #BREAK
  geom_boxplot(y = 0,
               width = 3,
               fill = "white",
               color = "black") #BREAK
```






---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
class: inverse, center, middle\n\n\n# and the mean of y\n')
```
---
class: inverse, center, middle


# and the mean of y



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("vizthemean2d", break_type = "user")`\n\n```{r vizthemean2d, include = F}\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  drop_na() %>% \n  ggplot() +\n  aes(x = bill_length_mm) +\n  aes(y = flipper_length_mm) +\n  geom_point() + #BREAK\n  geom_xmean() + #BREAK\n  geom_ymean() + #BREAK\n  aes(color = species) + #BREAK\n  facet_wrap(facets = vars(species)) + #BREAK\n  facet_grid(cols = vars(species),\n             rows = vars(sex)) #BREAK\n```\n')
```
---

`r chunk_reveal("vizthemean2d", break_type = "user")`

```{r vizthemean2d, include = F}
library(ggxmean)
palmerpenguins::penguins %>% 
  drop_na() %>% 
  ggplot() +
  aes(x = bill_length_mm) +
  aes(y = flipper_length_mm) +
  geom_point() + #BREAK
  geom_xmean() + #BREAK
  geom_ymean() + #BREAK
  aes(color = species) + #BREAK
  facet_wrap(facets = vars(species)) + #BREAK
  facet_grid(cols = vars(species),
             rows = vars(sex)) #BREAK
```



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
class: inverese, center, middle\n\n# OLS\n\n\n')
```
---
class: inverese, center, middle

# OLS





---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("ols", break_type = "user")`\n\n```{r ols, include = F}\nggxmean:::geoms_chalk()  # let the default color be chaulky\npalmerpenguins::penguins %>% \n  filter(species == "Chinstrap" & sex == "male") %>% \n  ggplot() +\n  ggxmean:::theme_chalkboard_slate() + \n  aes(x = flipper_length_mm) +\n  aes(y = body_mass_g) +\n  geom_point() + #BREAK\n  ggxmean:::geom_lm() + #BREAK\n  geom_rug(aes(y = NULL)) + #BREAK\n  geom_xvline(alpha = .1,  \n                        linetype = "dotted") + #BREAK\n  ggxmean:::geom_lmfitted(color = "blue", size = 2.5) + #BREAK\n  ggxmean:::geom_lmresiduals(color = "tomato3") + #BREAK\n  geom_ymean() + #BREAK\n  geom_xmean() + #BREAK\n  ggxmean:::geom_xymean(size = 3, color = "lightpink4") + #BREAK\n  ggxmean:::geom_lmformula() + #BREAK\n  # plug and chug to calculate an \n  # expected value of y for a given x \n  annotate(geom = "point",  \n           x = 208,  \n           y = 40.3 * 208 - 4110,  \n           size = 5, \n           shape = "diamond") + #BREAK\n  ggxmean:::geom_lmrun(color = "violetred4") + #BREAK\n  ggxmean:::geom_lmrise(color = "violetred4") + #BREAK\n  ggxmean:::geom_lmrun10(color = "chartreuse3") + #BREAK\n  ggxmean:::geom_lmrise10(color = "chartreuse3") + #BREAK\n  ggxmean:::geom_lmpredictx(alpha = .2) + #BREAK\n  ggxmean:::geom_lmpredicty(alpha = .2) + #BREAK\n  ggxmean:::geom_lmintercept() + #BREAK\n  ggxmean:::geom_lminterceptcoords(hjust = 0) #BREAK\n```\n\n')
```
---

`r chunk_reveal("ols", break_type = "user")`

```{r ols, include = F}
ggxmean:::geoms_chalk()  # let the default color be chaulky
palmerpenguins::penguins %>% 
  filter(species == "Chinstrap" & sex == "male") %>% 
  ggplot() +
  ggxmean:::theme_chalkboard_slate() + 
  aes(x = flipper_length_mm) +
  aes(y = body_mass_g) +
  geom_point() + #BREAK
  ggxmean:::geom_lm() + #BREAK
  geom_rug(aes(y = NULL)) + #BREAK
  geom_xvline(alpha = .1,  
                        linetype = "dotted") + #BREAK
  ggxmean:::geom_lmfitted(color = "blue", size = 2.5) + #BREAK
  ggxmean:::geom_lmresiduals(color = "tomato3") + #BREAK
  geom_ymean() + #BREAK
  geom_xmean() + #BREAK
  ggxmean:::geom_xymean(size = 3, color = "lightpink4") + #BREAK
  ggxmean:::geom_lmformula() + #BREAK
  # plug and chug to calculate an 
  # expected value of y for a given x 
  annotate(geom = "point",  
           x = 208,  
           y = 40.3 * 208 - 4110,  
           size = 5, 
           shape = "diamond") + #BREAK
  ggxmean:::geom_lmrun(color = "violetred4") + #BREAK
  ggxmean:::geom_lmrise(color = "violetred4") + #BREAK
  ggxmean:::geom_lmrun10(color = "chartreuse3") + #BREAK
  ggxmean:::geom_lmrise10(color = "chartreuse3") + #BREAK
  ggxmean:::geom_lmpredictx(alpha = .2) + #BREAK
  ggxmean:::geom_lmpredicty(alpha = .2) + #BREAK
  ggxmean:::geom_lmintercept() + #BREAK
  ggxmean:::geom_lminterceptcoords(hjust = 0) #BREAK
```




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
class: inverse\n\n# Correlation\n\n--\n\n# Don\'t worry about the overall importance of the problem; \n--\nwork on it if it looks interesting.  \n--\nI think there\'s a sufficient correlation between interest and importance.  \n--\n- David Blackwell\n\n\n\n')
```
---
class: inverse

# Correlation

--

# Don't worry about the overall importance of the problem; 
--
work on it if it looks interesting.  
--
I think there's a sufficient correlation between interest and importance.  
--
- David Blackwell






---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("vizthecorrelation", break_type = "user")`\n\n```{r vizthecorrelation, include=F}\nggxmean:::geoms_chalk()  # let the default aesthetics be chalky\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  mutate(id = row_number()) %>% \n  ggplot() + \n  aes(x = bill_length_mm) +\n  aes(y = flipper_length_mm) + \n  geom_point() + \n  ggxmean:::theme_chalkboard() + #BREAK\n  geom_xmean() + #BREAK\n  geom_ymean() + #BREAK\n  ggxmean:::geom_yhline(alpha = .02) + #BREAK\n  ggxmean:::geom_xvline(alpha = .02) + #BREAK\n  ggxmean:::geom_xdiff() + #BREAK\n  ggxmean:::geom_ydiff() + #BREAK\n  ggxmean:::geom_diffsmultiplied() + #BREAK\n  ggxmean:::geom_x1sd() + #BREAK\n  ggxmean:::geom_y1sd() + #BREAK\n  ggxmean:::geom_rsq1(fill = "blue") + #BREAK\n  ggxmean:::geom_xy1sd(fill = "green") + #BREAK\n  ggxmean:::geom_xydiffsmean(alpha = 1,\n                   fill = "plum3") + \n  ggxmean:::geom_corrlabel() + #BREAK\n  ggxmean:::geom_lm() + #BREAK\n  facet_wrap(facet = vars(species)) #BREAK\n```\n\n')
```
---

`r chunk_reveal("vizthecorrelation", break_type = "user")`

```{r vizthecorrelation, include=F}
ggxmean:::geoms_chalk()  # let the default aesthetics be chalky
library(ggxmean)
palmerpenguins::penguins %>% 
  mutate(id = row_number()) %>% 
  ggplot() + 
  aes(x = bill_length_mm) +
  aes(y = flipper_length_mm) + 
  geom_point() + 
  ggxmean:::theme_chalkboard() + #BREAK
  geom_xmean() + #BREAK
  geom_ymean() + #BREAK
  ggxmean:::geom_yhline(alpha = .02) + #BREAK
  ggxmean:::geom_xvline(alpha = .02) + #BREAK
  ggxmean:::geom_xdiff() + #BREAK
  ggxmean:::geom_ydiff() + #BREAK
  ggxmean:::geom_diffsmultiplied() + #BREAK
  ggxmean:::geom_x1sd() + #BREAK
  ggxmean:::geom_y1sd() + #BREAK
  ggxmean:::geom_rsq1(fill = "blue") + #BREAK
  ggxmean:::geom_xy1sd(fill = "green") + #BREAK
  ggxmean:::geom_xydiffsmean(alpha = 1,
                   fill = "plum3") + 
  ggxmean:::geom_corrlabel() + #BREAK
  ggxmean:::geom_lm() + #BREAK
  facet_wrap(facet = vars(species)) #BREAK
```




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
class: inverse, center\n\n# A behavior that is a little weird:  the vline at x requires y to exist\n\n--\n\n## This is because the verticle line inherits from segment, and y is Inf and yend is -Inf.  W/o some kind of y scale, we don\'t see anything. \n\n--\n\n## This is true of other vline and hline geoms too geom_xmin, geom_ymin, geom_xvline, etc\n')
```
---
class: inverse, center

# A behavior that is a little weird:  the vline at x requires y to exist

--

## This is because the verticle line inherits from segment, and y is Inf and yend is -Inf.  W/o some kind of y scale, we don't see anything. 

--

## This is true of other vline and hline geoms too geom_xmin, geom_ymin, geom_xvline, etc



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("suprising")`\n\n```{r suprising, include = F}\nggxmean:::geoms_chalk()\ncars %>% \n  ggplot() +\n  ggxmean:::theme_chalkboard_slate() + \n  aes(x = speed) +\n  # we dont see it\n  geom_xmean() +\n  # only x aes is required for xmean \n  # by y is set to neg Inf and pos Inf\n  # means y needs activated\n  aes(y = dist) +\n  geom_blank() +\n  geom_point() + \n  geom_rug()\n```\n')
```
---

`r chunk_reveal("suprising")`

```{r suprising, include = F}
ggxmean:::geoms_chalk()
cars %>% 
  ggplot() +
  ggxmean:::theme_chalkboard_slate() + 
  aes(x = speed) +
  # we dont see it
  geom_xmean() +
  # only x aes is required for xmean 
  # by y is set to neg Inf and pos Inf
  # means y needs activated
  aes(y = dist) +
  geom_blank() +
  geom_point() + 
  geom_rug()
```

