---
title: "Template Title"
author: "Your Name"
date: "The Date"
output: 
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
title: "Template Title"\nauthor: "Your Name"\ndate: "The Date"\noutput: \n  xaringan::moon_reader:\n    lib_dir: libs\n    css: [default, hygge, ninjutsu]\n    nature:\n      ratio: 16:9\n      highlightStyle: github\n      highlightLines: true\n      countIncrementalSlides: false')
```


---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\n```{r, include = F}\n# This is the recommended set up for flipbooks\n# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming\nknitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = F)\nlibrary(flipbookr)\nlibrary(tidyverse)\n\n```\n\n\n')
```
---


```{r, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = F)
library(flipbookr)
library(tidyverse)

```





---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n# viz the means and conditional means\n\n')
```
---

# viz the means and conditional means




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\n`r chunk_reveal("vizthemean1d")`\n\n```{r vizthemean1d, include = F}\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  drop_na() %>% \n  ggplot() +\n  aes(x = bill_length_mm) +\n  geom_rug(alpha = .3) +\n  geom_histogram(alpha = .4) +\n  ggxmean:::geom_xmean() +\n  aes(fill = species) + # unexpected behavior here\n  aes(color = species) +\n  facet_wrap(facets = vars(species)) +\n  facet_grid(cols = vars(species),\n             rows = vars(sex))\n```\n\n\n\n')
```
---


`r chunk_reveal("vizthemean1d")`

```{r vizthemean1d, include = F}
library(ggxmean)
palmerpenguins::penguins %>% 
  drop_na() %>% 
  ggplot() +
  aes(x = bill_length_mm) +
  geom_rug(alpha = .3) +
  geom_histogram(alpha = .4) +
  ggxmean:::geom_xmean() +
  aes(fill = species) + # unexpected behavior here
  aes(color = species) +
  facet_wrap(facets = vars(species)) +
  facet_grid(cols = vars(species),
             rows = vars(sex))
```






---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\n`r chunk_reveal("vizthemean2d")`\n\n```{r vizthemean2d, include = F}\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  drop_na() %>% \n  ggplot() +\n  aes(x = bill_length_mm) +\n  aes(y = flipper_length_mm) +\n  geom_point() +\n  ggxmean:::geom_xmean() +\n  aes(color = species) +\n  facet_wrap(facets = vars(species)) +\n  ggxmean:::geom_ymean() +\n  facet_grid(cols = vars(species),\n             rows = vars(sex))\n```\n\n\n\n')
```
---


`r chunk_reveal("vizthemean2d")`

```{r vizthemean2d, include = F}
library(ggxmean)
palmerpenguins::penguins %>% 
  drop_na() %>% 
  ggplot() +
  aes(x = bill_length_mm) +
  aes(y = flipper_length_mm) +
  geom_point() +
  ggxmean:::geom_xmean() +
  aes(color = species) +
  facet_wrap(facets = vars(species)) +
  ggxmean:::geom_ymean() +
  facet_grid(cols = vars(species),
             rows = vars(sex))
```






---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\n`r chunk_reveal("vizthecorrelation", title = "## viz the correlation")`\n\n```{r vizthecorrelation, include=F}\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  drop_na() %>% \n  ggplot() +\n  aes(x = bill_length_mm) +\n  aes(y = flipper_length_mm) +\n  geom_point() +\n  ggxmean:::geom_xmean() +\n  ggxmean:::geom_ymean() +\n  ggxmean:::geom_yhline(alpha = .02) +\n  ggxmean:::geom_xvline(alpha = .02) +\n  ggxmean:::geom_xdiff() +\n  ggxmean:::geom_ydiff() +\n  ggxmean:::geom_diffsmultiplied() +\n  aes(x = ((bill_length_mm - mean(bill_length_mm)) / sd(bill_length_mm))) +\n  aes(y = (flipper_length_mm - mean(flipper_length_mm))/sd(flipper_length_mm))\n```\n')
```
---


`r chunk_reveal("vizthecorrelation", title = "## viz the correlation")`

```{r vizthecorrelation, include=F}
library(ggxmean)
palmerpenguins::penguins %>% 
  drop_na() %>% 
  ggplot() +
  aes(x = bill_length_mm) +
  aes(y = flipper_length_mm) +
  geom_point() +
  ggxmean:::geom_xmean() +
  ggxmean:::geom_ymean() +
  ggxmean:::geom_yhline(alpha = .02) +
  ggxmean:::geom_xvline(alpha = .02) +
  ggxmean:::geom_xdiff() +
  ggxmean:::geom_ydiff() +
  ggxmean:::geom_diffsmultiplied() +
  aes(x = ((bill_length_mm - mean(bill_length_mm)) / sd(bill_length_mm))) +
  aes(y = (flipper_length_mm - mean(flipper_length_mm))/sd(flipper_length_mm))
```



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("suprising", title = "## something surprising")`\n\n```{r suprising, include = F}\ncars %>% \n  ggplot() +\n  aes(x = speed) +\n  ggxmean:::geom_xmean(color = "firebrick",\n             size = 2,\n             linetype = "dotted") +\n  # only x aes is required for xmean \n  # by y is set to neg Inf and pos Inf\n  # means y needs activated\n  aes(y = dist) +\n  geom_blank() +\n  geom_point() + \n  geom_rug()\n```\n\n\n')
```
---

`r chunk_reveal("suprising", title = "## something surprising")`

```{r suprising, include = F}
cars %>% 
  ggplot() +
  aes(x = speed) +
  ggxmean:::geom_xmean(color = "firebrick",
             size = 2,
             linetype = "dotted") +
  # only x aes is required for xmean 
  # by y is set to neg Inf and pos Inf
  # means y needs activated
  aes(y = dist) +
  geom_blank() +
  geom_point() + 
  geom_rug()
```



