---
title: "{ggxmean}"
author: "Your Name"
date: "The Date"
output: 
  xaringan::moon_reader:
    lib_dir: libs
    seal: FALSE
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
title: "{ggxmean}"\nauthor: "Your Name"\ndate: "The Date"\noutput: \n  xaringan::moon_reader:\n    lib_dir: libs\n    seal: FALSE\n    css: [default, hygge, ninjutsu]\n    nature:\n      ratio: 16:9\n      highlightStyle: github\n      highlightLines: true\n      countIncrementalSlides: false')
```


---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\nclass: inverse\nbackground-image: url(https://images.unsplash.com/photo-1572291720677-d8d28ac52a5b?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1556&q=80)\nbackground-size: cover\n\n# [{ggxmean}](https://github.com/EvaMaeRey/ggxmean)\n<br><br><br><br><br>\n<br><br><br><br><br>\n<br><br><br><br><br>\n<br><br><br><br><br>\n#### Photo credit: Hans Veth\n\n\n```{r, include = F}\n# This is the recommended set up for flipbooks\n# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming\nknitr::opts_chunk$set(fig.width = 8, message = FALSE, warning = FALSE, comment = "", cache = T)\nlibrary(flipbookr)\nlibrary(tidyverse)\n\n```\n\n\n')
```
---


class: inverse
background-image: url(https://images.unsplash.com/photo-1572291720677-d8d28ac52a5b?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1556&q=80)
background-size: cover

# [{ggxmean}](https://github.com/EvaMaeRey/ggxmean)
<br><br><br><br><br>
<br><br><br><br><br>
<br><br><br><br><br>
<br><br><br><br><br>
#### Photo credit: Hans Veth


```{r, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 8, message = FALSE, warning = FALSE, comment = "", cache = T)
library(flipbookr)
library(tidyverse)

```





---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n# viz the means and conditional means\n\n')
```
---

# viz the means and conditional means




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\n`r chunk_reveal("vizthemean1d", break_type = "user")`\n\n```{r vizthemean1d, include = F}\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  drop_na() %>% \n  ggplot() +\n  aes(x = bill_length_mm) +\n  geom_rug(alpha = .3) +\n  geom_histogram(alpha = .4) + #BREAK\n  ggxmean:::geom_xmean() + #BREAK\n  # unexpected behavior here\n  aes(fill = species) + #BREAK\n  aes(color = species) + #BREAK\n  facet_grid(rows = vars(species)) + #BREAK\n  facet_grid(rows = vars(species, sex)) + #BREAK\n  geom_xq2575(linetype = "dotted") + #BREAK\n  geom_xmin(linetype = "solid") + #BREAK\n  geom_xmax(linetype = "solid",\n            color = "goldenrod") #BREAK\n```\n\n\n\n')
```
---


`r chunk_reveal("vizthemean1d", break_type = "user")`

```{r vizthemean1d, include = F}
library(ggxmean)
palmerpenguins::penguins %>% 
  drop_na() %>% 
  ggplot() +
  aes(x = bill_length_mm) +
  geom_rug(alpha = .3) +
  geom_histogram(alpha = .4) + #BREAK
  ggxmean:::geom_xmean() + #BREAK
  # unexpected behavior here
  aes(fill = species) + #BREAK
  aes(color = species) + #BREAK
  facet_grid(rows = vars(species)) + #BREAK
  facet_grid(rows = vars(species, sex)) + #BREAK
  ggxmean:::geom_xq2575(linetype = "dotted") + #BREAK
  ggxmean:::geom_xmin(linetype = "solid") + #BREAK
  ggxmean:::geom_xmax(linetype = "solid",
            color = "goldenrod") #BREAK
```






---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("vizthemean2d", break_type = "user")`\n\n```{r vizthemean2d, include = F}\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  drop_na() %>% \n  ggplot() +\n  aes(x = bill_length_mm) +\n  aes(y = flipper_length_mm) +\n  geom_point() + #BREAK\n  ggxmean:::geom_xmean() + #BREAK\n  aes(color = species) + #BREAK\n  facet_wrap(facets = vars(species)) + #BREAK\n  ggxmean:::geom_ymean() + #BREAK\n  facet_grid(cols = vars(species),\n             rows = vars(sex)) #BREAK\n```\n\n\n\n')
```
---

`r chunk_reveal("vizthemean2d", break_type = "user")`

```{r vizthemean2d, include = F}
library(ggxmean)
palmerpenguins::penguins %>% 
  drop_na() %>% 
  ggplot() +
  aes(x = bill_length_mm) +
  aes(y = flipper_length_mm) +
  geom_point() + #BREAK
  ggxmean:::geom_xmean() + #BREAK
  aes(color = species) + #BREAK
  facet_wrap(facets = vars(species)) + #BREAK
  ggxmean:::geom_ymean() + #BREAK
  facet_grid(cols = vars(species),
             rows = vars(sex)) #BREAK
```






---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\n`r chunk_reveal("vizthecorrelation", title = "## viz the correlation" , break_type = "user")`\n\n```{r vizthecorrelation, include=F}\nlibrary(ggxmean)\npalmerpenguins::penguins %>% \n  drop_na() %>% \n  ggplot() +\n  aes(x = bill_length_mm) +\n  aes(y = flipper_length_mm) + \n  geom_point() + #BREAK\n  ggxmean:::geom_xmean() + #BREAK\n  ggxmean:::geom_ymean() + #BREAK\n  ggxmean:::geom_yhline(alpha = .02) + #BREAK\n  ggxmean:::geom_xvline(alpha = .02) + #BREAK\n  ggxmean:::geom_xdiff() + #BREAK\n  ggxmean:::geom_ydiff() + #BREAK\n  ggxmean:::geom_diffsmultiplied() + #BREAK\n  aes(x = ((bill_length_mm - mean(bill_length_mm)) / sd(bill_length_mm))) + #BREAK\n  aes(y = (flipper_length_mm - mean(flipper_length_mm))/sd(flipper_length_mm)) #BREAK\n```\n')
```
---


`r chunk_reveal("vizthecorrelation", title = "## viz the correlation" , break_type = "user")`

```{r vizthecorrelation, include=F}
library(ggxmean)
palmerpenguins::penguins %>% 
  drop_na() %>% 
  ggplot() +
  aes(x = bill_length_mm) +
  aes(y = flipper_length_mm) + 
  geom_point() + #BREAK
  ggxmean:::geom_xmean() + #BREAK
  ggxmean:::geom_ymean() + #BREAK
  ggxmean:::geom_yhline(alpha = .02) + #BREAK
  ggxmean:::geom_xvline(alpha = .02) + #BREAK
  ggxmean:::geom_xdiff() + #BREAK
  ggxmean:::geom_ydiff() + #BREAK
  ggxmean:::geom_diffsmultiplied() + #BREAK
  aes(x = ((bill_length_mm - mean(bill_length_mm)) / sd(bill_length_mm))) + #BREAK
  aes(y = (flipper_length_mm - mean(flipper_length_mm))/sd(flipper_length_mm)) #BREAK
```



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("suprising", title = "### something surprising")`\n\n```{r suprising, include = F}\ncars %>% \n  ggplot() +\n  aes(x = speed) +\n  # we dont see it\n  ggxmean:::geom_xmean(color = "firebrick",\n             size = 2,\n             linetype = "dotted") +\n  # only x aes is required for xmean \n  # by y is set to neg Inf and pos Inf\n  # means y needs activated\n  aes(y = dist) +\n  geom_blank() +\n  geom_point() + \n  geom_rug()\n```\n')
```
---

`r chunk_reveal("suprising", title = "### something surprising")`

```{r suprising, include = F}
cars %>% 
  ggplot() +
  aes(x = speed) +
  # we dont see it
  ggxmean:::geom_xmean(color = "firebrick",
             size = 2,
             linetype = "dotted") +
  # only x aes is required for xmean 
  # by y is set to neg Inf and pos Inf
  # means y needs activated
  aes(y = dist) +
  geom_blank() +
  geom_point() + 
  geom_rug()
```



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("ols")`\n\n```{r ols, include = F}\npalmerpenguins::penguins %>% \n  filter(species == "Chinstrap") %>% \n  filter(sex == "male") %>% \n  ggplot() +\n  aes(x = flipper_length_mm) +\n  aes(y = body_mass_g) +\n  geom_point() +\n  ggxmean:::geom_lm() +\n  geom_rug(aes(y = NULL)) + \n  ggxmean:::geom_xvline(alpha = .1, \n                        linetype = "dotted") +\n  ggxmean:::geom_lmfitted(color = "blue",    \n                          size = 2) +\n  ggxmean:::geom_lmresiduals(linetype = "dashed", \n                             color = "firebrick") +\n  ggxmean:::geom_ymean() +\n  ggxmean:::geom_xmean() +\n  geom_xymean(size = 3, color = "magenta") +\n  ggxmean:::geom_lmformula() +\n  ggxmean:::geom_lmrun(color = "magenta") +\n  ggxmean:::geom_lmrise(color = "magenta") +\n  ggxmean:::geom_lmintercept()\n```\n\n')
```
---

`r chunk_reveal("ols")`

```{r ols, include = F}
palmerpenguins::penguins %>% 
  filter(species == "Chinstrap") %>% 
  filter(sex == "male") %>% 
  ggplot() +
  aes(x = flipper_length_mm) +
  aes(y = body_mass_g) +
  geom_point() +
  ggxmean:::geom_lm() +
  geom_rug(aes(y = NULL)) + 
  ggxmean:::geom_xvline(alpha = .1, 
                        linetype = "dotted") +
  ggxmean:::geom_lmfitted(color = "blue",    
                          size = 2) +
  ggxmean:::geom_lmresiduals(linetype = "dashed", 
                             color = "firebrick") +
  ggxmean:::geom_ymean() +
  ggxmean:::geom_xmean() +
  ggxmean:::geom_xymean(size = 3, color = "magenta") +
  ggxmean:::geom_lmformula() +
  ggxmean:::geom_lmrun(color = "magenta") +
  ggxmean:::geom_lmrise(color = "magenta") +
  ggxmean:::geom_lmintercept()
```


