---
title: "A Python Flipbook"
subtitle: "With {flipbookr} and xaringan"
author: "Gina Reynolds, March 2020"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:10
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
title: "A Python Flipbook"\nsubtitle: "With {flipbookr} and xaringan"\nauthor: "Gina Reynolds, March 2020"\noutput:\n  xaringan::moon_reader:\n    lib_dir: libs\n    css: [default, hygge, ninjutsu]\n    nature:\n      ratio: 16:10\n      highlightStyle: github\n      highlightLines: true\n      countIncrementalSlides: false')
```


---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\nThis is pretty experimental work.  The python "parser" (basically no parsing) means there are strong constraints on code.  Each new line must yield complete code statement...  \n\n\n```{r, include = F}\n# This is the recommended set up for flipbooks\n# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming\nknitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = F, dev = "svg", fig.ext = "svg")\nlibrary(flipbookr)\nlibrary(tidyverse)\n```\n\n\n<!-- This next chunk is just for the developer -- working w/ local code -->\n\n```{r just_for_evamaerey, cache = FALSE, echo = FALSE, eval = T}\ntry(source("../../../../../R/a_create_test_code.R"))\ntry(source("../../../../../R/b_parsing.R"))\ntry(source("../../../../../R/c_prep_sequences.R"))\ntry(source("../../../../../R/d_prep_rmd_chunks.R"))\ntry(source("../../../../../R/e_define_css.R"))\ntry(source("../../../../../R/f_chunk_expand.R"))\ntry(source("../../../../../R/g_exported_functions.R"))\ntry(source("../../../../../R/h_write_instant_flipbook.R.R"))\n```\n\n')
```
---


This is pretty experimental work.  The python "parser" (basically no parsing) means there are strong constraints on code.  Each new line must yield complete code statement...  


```{r, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = F, dev = "svg", fig.ext = "svg")
library(flipbookr)
library(tidyverse)
```


<!-- This next chunk is just for the developer -- working w/ local code -->

```{r just_for_evamaerey, cache = FALSE, echo = FALSE, eval = T}
try(source("../../../../../R/a_create_test_code.R"))
try(source("../../../../../R/b_parsing.R"))
try(source("../../../../../R/c_prep_sequences.R"))
try(source("../../../../../R/d_prep_rmd_chunks.R"))
try(source("../../../../../R/e_define_css.R"))
try(source("../../../../../R/f_chunk_expand.R"))
try(source("../../../../../R/g_exported_functions.R"))
try(source("../../../../../R/h_write_instant_flipbook.R.R"))
```




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("hello_python", lang = "python")`\n\n\n```{python hello_python, include = F}\n[1, 4] * 8\n\n3 + 4 * 8 \n\n2 + 6\n\n4 * 8\n\n[1,2] + [3,4,5,6]\n\n["hello", "world!", 1, 2, 3] * 2\n\nimport numpy as np\n\nnp.reshape(np.arange(1,25), \n    (4,3,2), "F")\n```\n')
```
---

`r chunk_reveal("hello_python", lang = "python")`


```{python hello_python, include = F}
[1, 4] * 8

3 + 4 * 8 

2 + 6

4 * 8

[1,2] + [3,4,5,6]

["hello", "world!", 1, 2, 3] * 2

import numpy as np

np.reshape(np.arange(1,25), 
    (4,3,2), "F")
```



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("simple_plot", lang = "python", widths = c(59,40))`\n\n\n```{python simple_plot, include = F}\nimport matplotlib.pyplot as plt\nyear = [1950, 1970, \n  1990, 2010]\npop = [2.519, 3, 5, 6]\nplt.plot(year, pop); plt.show()\n```\n\n\n\n')
```
---

`r chunk_reveal("simple_plot", lang = "python", widths = c(59,40))`


```{python simple_plot, include = F}
import matplotlib.pyplot as plt
year = [1950, 1970, 
  1990, 2010]
pop = [2.519, 3, 5, 6]
plt.plot(year, pop); plt.show()
```






---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("numpy", lang = "python")`\n\n\n```{python numpy, include = F}\n# import pandas as pd\nimport matplotlib.pyplot as plt\nimport numpy as np\nt = np.arange(0, 2, .05)\nt\ns = np.sin(2*np.pi*t)\ns\n```\n\n')
```
---

`r chunk_reveal("numpy", lang = "python")`


```{python numpy, include = F}
# import pandas as pd
import matplotlib.pyplot as plt
import numpy as np
t = np.arange(0, 2, .05)
t
s = np.sin(2*np.pi*t)
s
```




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("numpy2", lang = "python")`\n\n\n```{python numpy2, include = F}\nplt.plot(t, s)\nplt.xlabel(\'time (s)\')\nplt.ylabel(\'voltage (mV)\')\nplt.grid(True); plt.show()\n```\n\n')
```
---

`r chunk_reveal("numpy2", lang = "python")`


```{python numpy2, include = F}
plt.plot(t, s)
plt.xlabel('time (s)')
plt.ylabel('voltage (mV)')
plt.grid(True); plt.show()
```




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\nCredit to matplotlib.org for this example!\n')
```
---

Credit to matplotlib.org for this example!



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n\n`r chunk_reveal("prep", lang = "python", break_type = 1)`\n\n```{python prep, include = F}\nimport numpy as np  \nimport pandas as pd \n\nstudent_scores = pd.DataFrame(\n{"student": ["Andy", "Bernie", "Cindy", "Deb"],\n"sex": ["M", "M", "F", "F"],\n"english": [98, 95, 70, 40], # eng grades\n"math": [66, 89, 60, 70], # math grades\n"physics": [78, 90, 92, 88] # physics grades\n}) \n\nstudent_scores \n```\n\n')
```
---


`r chunk_reveal("prep", lang = "python", break_type = 1)`

```{python prep, include = F}
import numpy as np  
import pandas as pd 

student_scores = pd.DataFrame(
{"student": ["Andy", "Bernie", "Cindy", "Deb"],
"sex": ["M", "M", "F", "F"],
"english": [98, 95, 70, 40], # eng grades
"math": [66, 89, 60, 70], # math grades
"physics": [78, 90, 92, 88] # physics grades
}) 

student_scores 
```




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n## Now lets find the highest three grades among all of these grades.  This is done by reshaping the data, sorting it decending order, and selecting the top three rows. \n')
```
---

## Now lets find the highest three grades among all of these grades.  This is done by reshaping the data, sorting it decending order, and selecting the top three rows. 



---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("bam", lang = "python", widths = c(1,1))`\n\n```{python bam, include = F}\nstudent_scores \\n  .melt(id_vars=[\'student\', "sex"], \n        var_name="subject", \n        value_name="final_grade") \\n  .sort_values(by=[\'final_grade\'], ascending=False) \\n  .head(3)\n```\n\n')
```
---

`r chunk_reveal("bam", lang = "python", widths = c(1,1))`

```{python bam, include = F}
student_scores \
  .melt(id_vars=['student', "sex"], 
        var_name="subject", 
        value_name="final_grade") \
  .sort_values(by=['final_grade'], ascending=False) \
  .head(3)
```




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\nThe last example owes thanks Suraj Thapa for sketching out ideas these ideas!\n\n')
```
---

The last example owes thanks Suraj Thapa for sketching out ideas these ideas!




---
class: inverse

###From source .Rmd:

 ```{r, comment = '', echo = F, return = 'asis'}
cat('---
\n`r chunk_reveal("def", lang = "python", title = "## Code by Malia!")`\n\n```{python def, include = F}\ndef flower(like):\n  print("I like flowers " + like)\n\nflower("that are red.")\nflower("that smell good.")\n\ndef strawberry(sweet):\n  print("strawberrys are sweet" + sweet)\n  \nstrawberry(", and red")  \n```\n\n\n\n\n\n\n```{css, eval = TRUE, echo = FALSE}\n.remark-code{line-height: 1.5; font-size: 80%}\n\n@media print {\n  .has-continuation {\n    display: block;\n  }\n}\n```')
```
---

`r chunk_reveal("def", lang = "python", title = "## Code by Malia!")`

```{python def, include = F}
def flower(like):
  print("I like flowers " + like)

flower("that are red.")
flower("that smell good.")

def strawberry(sweet):
  print("strawberrys are sweet" + sweet)
  
strawberry(", and red")  
```






```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 80%}

@media print {
  .has-continuation {
    display: block;
  }
}
```
